# Reproducible Research: Peer Assessment 1


## Loading and preprocessing the data
script to read de data set

```{r}
w<- read.csv("activity.csv",header=T,)
library(ggplot2)
library(lattice)
```

Explore and summarize the data

```{r}
str(w)
summary(w)
w$interval<- as.factor(w$interval)
```

agregate the data in days 

```{r}
d<- tapply(w$steps,w$date,na.rm=T, sum)
```

plot the histogram 

```{r}
hist(d, main="Number of steps per day", xlab="steps", col="red",breaks=5)
```


## What is mean total number of steps taken per day?

The mean and the median are: 
```{r}
mean(d, na.rm=T)
median(d,na.rm=T)
````


## What is the average daily activity pattern?

``
the average number of step in the 5 minutes interval is: 
```{r}
five<- tapply(w$steps, w$interval, na.rm=T, mean)
five<- as.data.frame(five)
five<- cbind(as.numeric(rownames(five)),five)
colnames(five)<- c("interval","steps")
````
Graphically the number of stpeps in the 5 minutes intervals.

```{r}
plot(five$interval,five$steps, type="l", 
     main="Mean of number of steps in 5 minutes interval",
     ylab="Steps", xlab="5 minutes interval", col="blue")

```
The five minutes interval with the maximun number of steps is
```{r}
five[five$steps==max(five$steps),1]
````

with the value of 

```{r}
max(five$steps)
```


## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
